---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "readme_figures/README-"
)
```

# policynet.terms: ERGM Terms for Policy Network Studies

## Updates
Package initialized. Nothing works yet, but will soon.

## About 

This package contains custom ERGM terms designed for use with policy networks. These terms of course can be used for other ERGMs as well.

## Installation

To install the package from [GitHub](https://github.com/tedhchen/policynet.terms), you will need the `devtools` package. If you are on a Windows machine, you will also need the standalone [Rtools](https://cran.r-project.org/bin/windows/Rtools/). If you do not already have the `network`, `ergm`, and `statnet.common` packages, installing `policynet.terms` will install them as well. 

Install the package by entering the following into your R console.
```{r, eval=F}
devtools::install_github("tedhchen/policynet.terms")
```




